---
title: "Benford's Law"
author: "Mike Nguyen"
date: "2/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)
```

-   Similar to Zipf's law: for a corpus of natural language: the frequency of any word is inversely proportional to its rank in the frequency table.

    -   Ex: The most frequent word will occur approximately twice as often as the second most frequent word, three times as often as the third most frequent word

-   **Newcomb--Benford law**, the **law of anomalous numbers**, or the **first-digit law**

    -   In any natural numerical data, the leading digit is likely to be small:

        -   The number 1 appears as leading significant about 30% of the time and so on.

Resources:

-   Example: <https://rstudio-pubs-static.s3.amazonaws.com/205239_5c34105c42b643259f2353762f31c330.html>
-   [Benford's law](https://en.wikipedia.org/wiki/Benford%27s_law#Scientific_fraud_detection)
-   [Fraud detection](https://en.wikipedia.org/wiki/Data_analysis_techniques_for_fraud_detection)

## Example 1

by [Nagdev Amruthnath](https://www.r-bloggers.com/2020/08/benfords-law-applying-to-existing-data/)

```{r}
# load libraries
library(gtrendsR)
library(reshape2)
library(dplyr)
library(benford.analysis)
# read data
data = read.csv("https://www2.census.gov/programs-surveys/popest/datasets/2010-2019/counties/totals/co-est2019-alldata.csv", header = T)
# filter out columns
data_filt = data %>% filter(COUNTY != 0) %>% select(c(STNAME, CTYNAME, CENSUS2010POP))
# perform benford analysis
trends = benford(data_filt$CENSUS2010POP, number.of.digits = 1, discrete = T, sign = "positive") 
trends
# plot results
plot(trends)
```

## Example 2

[original post](https://rstudio-pubs-static.s3.amazonaws.com/205239_5c34105c42b643259f2353762f31c330.html)

Benford function follows log base 10

```{r}
benlaw <- function(d)
  log10(1 + 1 / d)
digits <- 1:9
baseBarplot <-
  barplot(
    benlaw(digits),
    names.arg = digits,
    xlab = "First Digit",
    ylim = c(0, .35)
  )
```

```{r}
firstDigit <- function(x) substr(gsub('[0.]', '', x), 1, 1)
pctFirstDigit <- function(x) data.frame(table(firstDigit(x)) / length(x))
```

```{r}
N <- 1000
set.seed(1234)
x1 <- runif(N, 0, 100)
df1 <- pctFirstDigit(x1)
head(df1)
```

The value that you create will look very different from those from nature

```{r}
barplot(
    benlaw(digits),
    names.arg = digits,
    xlab = "First Digit",
    ylim = c(0, .35)
  )

lines(
  x = baseBarplot[, 1],
  y = df1$Freq,
  col = "red",
  lwd = 4,
  type = "b",
  pch = 23,
  cex = 1.5,
  bg = "red"
)


# When you square these values, it may resemble the Benford's law a little more

df2 <- pctFirstDigit(x1^2)
lines(x = baseBarplot[,1], y = df2$Freq, col = "violet", lwd = 4, 
      type = "b", pch = 23, cex = 1.5, bg = "violet")


# Then, you divide the original number with a newly generated dataset 


x3 <- runif(N, 0, 100)
df3 <- pctFirstDigit(x1^2 / x3)
lines(x = baseBarplot[,1], y = df3$Freq, col = "blue", lwd = 4, 
      type = "b", pch = 23, cex = 1.5, bg = "blue")

# then you time the newly generate dataset

x4 <- runif(N, 0, 100)
df4 <- pctFirstDigit(x1^2 / x3 * x4)
lines(x = baseBarplot[,1], y = df4$Freq, col = "green", lwd = 4, 
      type = "b", pch = 23, cex = 1.5, bg = "green")
```

Everything again with a legend

```{r}
library(ggplot2)
df <- data.frame(x = digits, y = benlaw(digits))
ggBarplot <- ggplot(df, aes(x = factor(x), y = y)) + geom_bar(stat = "identity") +
  xlab("First Digit") + ylab(NULL)
print(ggBarplot)

p1 <- ggBarplot + 
  geom_line(data = df1, 
            aes(x = Var1, y = Freq, group = 1), 
            colour = "red", 
            size = 2) +
  geom_point(data = df1, 
            aes(x = Var1, y = Freq, group = 1), 
            colour = "red", 
            size = 4, pch = 23, bg = "red")
p2 <- p1 +
  geom_line(data = df2, 
            aes(x = Var1, y = Freq, group = 1), 
            colour = "violet", 
            size = 2) +
  geom_point(data = df2, 
             aes(x = Var1, y = Freq, group = 1), 
             colour = "violet", 
             size = 4, pch = 23, bg = "violet")
print(p2)

DF <- cbind(df1, df2[2], df3[2], df4[2])
names(DF) <- c("FirstDigit", "X1", "X2=X1^2", "X3=X2 / X3", "X1^2 / X3 * X4")
head(DF)

library(reshape2)
mDF <- melt(DF, id = "FirstDigit", variable.name = "operation")
head(mDF)

P <- ggBarplot + 
  geom_line(data = mDF, 
            aes(x = FirstDigit, y = value, colour = operation, group = operation), 
            size = 1.5) +
  geom_point(data = mDF, 
            aes(x = FirstDigit, y = value, colour = operation, 
                group = operation, bg = operation), 
            size = 4, pch = 23)
print(P)
```

Moral of the story: Please don't try to fabricate data. Unless you have a sophisticated random number generator that can match the Benford's law, it's futile.
