---
title: "Independent t-test and Hypothesis Testing"
author: "Mike Nguyen"
output:
  pdf_document: default
  html_notebook: default
---

# Hypothesis Test

```{r, include = FALSE}
knitr::opts_chunk$set(warning = F, message = F)
```

## Visualization 1

```{r}
N = 20 #just chosen arbitrarily (20 responses)

samp = rnorm(N, mean = 0, sd = 1)

# hypothesis test whether the population mean is equal to 0. 
# null: the true population mean equals 0
# alternative: the true population mean is different from 0

myTest = t.test(samp, mu = 0, alternative = "two.sided")
myTest
# cannot reject the null

# get t-critical value (just like when you look up t-critical value)
tcrit = qt(0.025, df = (N - 1)) # alpha = 0.025

dum=seq(-3.5, 3.5, length=10^4) # For the plot


plot(dum, dt(dum, df=(N-1)), type='l', xlab='t', ylab='f(t)')
abline(v=myTest$statistic, lty=2)
abline(v=tcrit, col='red', lty=2)
abline(v=-tcrit, col='red', lty=2)
```

## Visualization 2

```{r}
library(MASS)
# real data
h=na.omit(survey$Height) # omit missing value in height

# say we know the true 
pop.mean=mean(h)
pop.mean

# but we can't survey everyone, so we only survey 30 people
h.sample = sample(h,30)
h.sample

# then we test whether the sample mean equals the true (population) mean
# null: the true population mean equals 172
# alternative: the true population mean is different from 172
t.test(h.sample,mu=pop.mean)
# cannot reject the null

# plot the t-test
library(gginference)
ggttest(t.test(h.sample,mu=pop.mean))
```

# Visualization 3

```{r}
library(MASS)
library(ggplot2)

h = na.omit(survey$Height)
pop.mean = mean(h) # true population mean

n_reps = 20 # try to sample 20 times
sample_size = 30 # in each sample we collect 30 repsonses 
res_list = list()

for (i in 1:n_reps) {
  h.sample = sample(h, sample_size)
  res_list[[i]] = t.test(h.sample, mu = pop.mean)
}

dat = data.frame(
  id = seq(length(res_list)),
  estimate = sapply(res_list, function(x)
    x$estimate),
  conf_int_lower = sapply(res_list, function(x)
    x$conf.int[1]),
  conf_int_upper = sapply(res_list, function(x)
    x$conf.int[2])
)

p = ggplot(data = dat, aes(x = estimate, y = id)) +
  geom_vline(xintercept = pop.mean,
             color = "red",
             linetype = 2) +
  geom_point(color = "grey30") +
  geom_errorbarh(
    aes(xmin = conf_int_lower, xmax = conf_int_upper),
    color = "grey30",
    height = 0.4
  )
p

# ggsave("CI_plot.png", plot=p, height=4, width=6, units="in", dpi=150)
```

# One sample t-test

Hypothesis test to see whether your mean is equal a hypothesized number

```{r}
library(webr)
library(moonBook)

set.seed(0)
treeVolume <- c(rnorm(75, mean = 36500, sd = 2000))
t.test(treeVolume, mu = 39000) # Ho: mu = 39000
plot(t.test(treeVolume, mu = 39000))
```

# Generate Data

```{r}
set.seed(0)

ClevelandSpending <- rnorm(50, mean = 250, sd = 75)
NYSpending <- rnorm(50, mean = 300, sd = 80)

spending <- c(ClevelandSpending, NYSpending)
city <- c(rep("Cleveland", 50), rep("New York", 50))

#Sample data
data = data.frame(spending = spending,
                  city = city)

# export data to excel
# rio::export(
#   cbind(ClevelandSpending, NYSpending),
#   file.path(getwd(), "lectures", "10", "independent_t.xlsx")
# )
```

# F-test for 2 variances

```{r}
library(webr)
library(moonBook)
var.test(ClevelandSpending, NYSpending)

# Alternatively 
F_test = var.test(data$spending ~ data$city, data = data)
plot(F_test)
```

# Two Sample t-test

## Equal Variances

```{r}
# Null: the two samples' means are equal 
# Ha: the sample
t.test(ClevelandSpending, NYSpending, var.equal = TRUE)
```

Equivalently,

```{r}
t.test(spending ~ city, var.equal = TRUE)
plot(t.test(spending ~ city, var.equal = TRUE))
```

## Unequal Variances

what if we have different variance for the two variables

```{r}
t.test(ClevelandSpending, NYSpending, var.equal = FALSE)
```

Alternatively,

```{r}
t.test(spending ~ city, var.equal = FALSE)
plot(t.test(spending ~ city, var.equal = FALSE))
```

## Visualization

### Density Plot

```{r}
library(ggplot2)
#Plot.
ggplot(data, aes(x = spending, fill = city)) + geom_density(alpha = 0.5)
```

## Boxplot

Plot weight by group and color by group

```{r}
library("ggpubr")
ggboxplot(
  data,
  x = "city",
  y = "spending",
  color = "city",
  palette = c("#00AFBB", "#E7B800"),
  ylab = "Weight",
  xlab = "Groups"
)

```
